---
title: "Assignment"
output: html_notebook
---

#On this first assignment, applying the basic functions of the Igraph package is required. The following datasets are #going to be #used:

#* Actors dataset - undirected graph - : For the 2005 Graph Drawing conference a data set was provided of the IMDB #movie database. 
#We will use a reduced version of this dataset, which derived all actor-actor collaboration edges where #the actors co-starred in at 
#least 2 movies together between 1995 and 2004. 

#You have to complete the code chunks in this document but also analyze the results, extract insights and answer the #short #questions. Fill the CSV attached with your answers, sometimes just the number is enough, some others just a #small sentence. Remember #to change the header with your email.

#In your submission please upload both the R Markdown and the CSV with the solutions.

# Loading data

#In this section, the goal is loading the datasets given, building the graph and analyzing basics metrics. Include the #edge or node attributes you consider.

#Describe the values provided by summary function on the graph object.
#*1) How many nodes are there?*
#*2) How many edges are there?*

```{r}
getwd()

library(readr)
library(ggplot2)
library(igraph)

edges <- read_tsv("imdb_actor_edges.tsv")

dim(edges)
head(edges)
class(edges)
#summary(edges)

key <- read_tsv("imdb_actors_key.tsv")

dim(key)
head(key)
class(key)
#summary(key)

g <- graph_from_data_frame(d = edges, directed = FALSE, vertices = key)

vcount(g)
ecount(g)
```
# Degree distribution

#Analyse the degree distribution. Compute the total degree distribution.
#*3) How does this distributions look like?*
#*4) What is the maximum degree?*
#*5) What is the minimum degree?*

```{r}
is.directed(g)
summary(g)

deg <- degree(g)

deg_dist <- degree.distribution(g)

plot(deg_dist,
     main = "degree distribution",
     xlab = "distribution",
     ylab = "frequency",
     col = "#296d98")

max(deg)
min(deg)

```
# Network Diameter and Average Path Length
#*6) What is the diameter of the graph?*
#*7) What is the avg path length of the graph?*

```{r}
diameter(g, directed = FALSE)

average.path.length(g, directed = FALSE)

```

# Node importance: Centrality measures

#Obtain the distribution of the number of movies made by an actor and the number of genres in which an actor starred in. It may be #useful to analyze and discuss the results to be obtained in the following exercises.

```{r}
V(g)
hist(V(g)$movies_95_04,
    main = "movies per actor",
    xlab = "number of movies",
    ylab = "frequency",
    labels = TRUE,
    col = "#296d98")

```

#Obtain three vectors with the degree, betweenness and closeness for each vertex of the actors' graph.

```{r}
deg <- degree(g)
head(deg, 5)

btw <- betweenness(g, v = V(g), normalized = TRUE)
head(btw, 5)

cl  <- closeness(g, v = V(g), normalized = TRUE)
head(cl, 5)

```

#Obtain the list of the 20 actors with the largest degree centrality. It can be useful to show a list with the degree, the name of #the actor, the number of movies, the main genre, and the number of genres in which the actor has participated.

#*8) Who is the actor with highest degree centrality?*
#*9) How do you explain the high degree of the top-20 list??*

```{r}
library(sqldf)
deg_cent<- sort(deg,decreasing=TRUE)[1:20]

deg_df <- as.data.frame(deg_cent)
deg_df <- cbind(Name=rownames(deg_df),deg_df)

deg_df2 <- sqldf("select a.*, b.id, b.movies_95_04, b.main_genre, b.genres from deg_df a left outer join key b on a.Name=b.name")

deg_df2

```

#Obtain the list of the 20 actors with the largest betweenness centrality. Show a list with the betweenness, the name of the actor, #the number of movies, the main genre, and the number of genres in which the actor has participated.

#*10) Who is the actor with highest betweennes?*
#*11) How do you explain the high betweenness of the top-20 list?*

```{r}
btw_cent <- sort(btw,decreasing=TRUE)[1:20]

btw_df <- as.data.frame(btw_cent)
btw_df <- cbind(Name=rownames(btw_df),btw_df)

btw_df2 <- sqldf("select a.*, b.id, b.movies_95_04, b.main_genre, b.genres from btw_df a left outer join key b on a.Name=b.name")

btw_df2

```

#Obtain the list of the 20 actors with the largest closeness centrality. Show a list with the closeness the name of the actor, the #number of movies, the main genre, and the number of genres in which the actor has participated.

#*12) Who is the actor with highest closeness centrality?*
#*13) How do you explain the high closeness of the top-20 list? *

```{r}
cl_cent <- sort(cl,decreasing=TRUE)[1:20]

cl_df <- as.data.frame(cl_cent)
cl_df <- cbind(Name=rownames(cl_df),cl_df)

cl_df2 <- sqldf("select a.*, b.id, b.movies_95_04, b.main_genre, b.genres from cl_df a left outer join key b on a.Name=b.name")

cl_df2

```

#Network Models (Optional)
#Explore the Erdös-Renyi model and compare its structural properties to those of real-world networks (actors):

```{r}
g_er <- erdos.renyi.game(17577,287074, type = "gnm")

plot(g_er, vertex.label= key, edge.arrow.size=0.02,vertex.size = 0.5, xlab = "Random Network: G(N,L) model")

```

* Degree distribution  P(k)
* Network Diameter and Average Path Length
* (Global and Local) Clustering Coefficient

#Comunity detection (Optional)
#Use any community detection algorithm for the actors' network and discuss whether the communities found make sense #according to the #vertex labels.